---
title: "MCNA 2022::Daily Monitoring Report"
author: "Mehedi Khan"
date: "`r Sys.time()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

<meta http-equiv="Content-Type" content="text/html;charset=UTF-8">
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("logo.jpg"),
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;')
```


```{r results="asis", echo=FALSE}
cat("
<style>
.leaflet-container {
    background: #FFF;
}
</style>
")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, cache = FALSE,comment = NA, message = FALSE, warning=FALSE, fig.align = 'center')




# read data
data <- read.csv("01_inputs/04_raw_data/hh.csv",stringsAsFactors = F,na.strings = c("", " ","9999",9999),encoding = "UTF-8") %>% rename(
  start = X.U.FEFF.start
)
indv <- read.csv("01_inputs/04_raw_data/indv.csv",stringsAsFactors = F,na.strings = c("", " ","9999",9999),encoding = "UTF-8") %>% rename(
  X_uuid = X_submission__uuid
)


total_survey <- nrow(data)
yes_consent <- data %>% filter(consent == "yes" ) %>% nrow() 
no_consent <- data %>% filter(consent == "no" ) %>% nrow() 
not_eleigible <- data %>% filter(calc_eligible == 0 ) %>% nrow() 

data <-  data %>% filter(consent == "yes" & calc_eligible == 1) # take only yes consent

eleigible <- data %>% filter(calc_eligible == 1 ) %>% nrow() 

# add population group
data <- data %>% mutate(
  pop_group = case_when(idp_camp == "yes" &  !is.na(camp_name) ~ "in_camp_idp",
                        calc_idp == 1 ~ "out_camp_idp",
                        calc_returnee == 1 ~ "returnee",
                        calc_host == 1 ~ "hc"),
  dis_rs = rowSums(data[c("calc_idp","calc_returnee","calc_host")],na.rm = T)
) %>% mutate(
  check_grp = case_when(dis_rs > 1 ~ "multiple_group",
                        dis_rs == 1  & idp_camp == "yes" ~ "multiple_group"),
  enumerator_name_id = case_when(ngo_name == "reach" ~ as.character(enumerator_num),
                                  T~as.character(enumerator_name))
)

group_by_pop_grp <- data %>% group_by(pop_group) %>% summarise(
  total_elegible = n()
)
if(TRUE %in% unique(is.na(data$pop_group))) {stop("you have NAs in group")}

if("multiple_group" %in% unique(data$check_grp) ) {stop("you have multiple group")}

########################################## Fix true district based one gps ##########################
admin_path <- "01_inputs/03_shapefile/"
admin3_boundary<- st_read(paste0(admin_path,"irq_admbnda_adm3_cso_20190603.shp")) %>% select(ends_with("_EN")) %>% rename(
  governorate_true = ADM1_EN,
  district_true = ADM2_EN,
  sub_district_true = ADM3_EN 
) %>% select(-ADM0_EN)

admin2_boundary <- st_read(paste0(admin_path,"irq_admbnda_adm2_cso_20190603.shp")) %>% select(ends_with("_EN")) %>% rename(
  governorate = ADM1_EN,
  district  = ADM2_EN
) %>% select(-ADM0_EN) %>% mutate(
   district = district %>% tolower() %>% str_replace_all("-","_") %>% str_replace_all(" ","_") %>% str_replace_all("'","")
)

df_for_true <- data %>% select(X_uuid,contains("gps"))
data_sf <- df_for_true %>% st_as_sf(coords = c("X_gpslocation_longitude","X_gpslocation_latitude"),crs = 4326)

df_with_adm <- data_sf %>% st_intersection(admin3_boundary) %>% as.data.frame() %>% select(-contains("gps"),-geometry)

data <- data %>% left_join(df_with_adm) %>% mutate(
  district = case_when(is.na(district_true)~ district_mcna, T ~ district_true),
  governorate = case_when(is.na(governorate_true)~ governorate_mcna, T ~ governorate_true),
)%>%  mutate(
  district = district %>% tolower() %>% str_replace_all("-","_") %>% str_replace_all(" ","_") %>% str_replace_all("'","")
)

########################################## sample frames ########################################################################

hc_sf <- read.csv("03_outputs/01_sampling/02_sampling/01_host_community/sampling_summary.csv") %>%
  rename(sample = X..surveys,
         buffer = X..buffer,
         district = Stratification,
         effective_sample =Effective.sample) %>% mutate(
           district = district %>% tolower() %>% str_replace_all("-","_") %>% str_replace_all(" ","_")
         ) %>% select(district,sample,effective_sample,buffer,Population)



returnees_sf<- read.csv("03_outputs/01_sampling/02_sampling/03_Returnees/sampling_summary.csv") %>%
  rename(sample = X..surveys,
         buffer = X..buffer,
         district = Stratification,
         effective_sample =Effective.sample) %>% select(district,sample,effective_sample,buffer,Population)%>% mutate(
           district = district %>% tolower() %>% str_replace_all("-","_") %>% str_replace_all(" ","_") %>% str_replace_all("'","")
         ) 


out_idp_sf <- read.csv("03_outputs/01_sampling/02_sampling/02_IDPs/01_out_camp/sampling_summary.csv") %>%
  rename(sample = X..surveys,
         buffer = X..buffer,
         district = Stratification,
         effective_sample =Effective.sample) %>% select(district,sample,effective_sample,buffer,Population)%>% mutate(
           district = district %>% tolower() %>% str_replace_all("-","_") %>% str_replace_all(" ","_")  %>% str_replace_all("'","")
         ) 


in_idp_sf <- read.csv("03_outputs/01_sampling/02_sampling/02_IDPs/02_in_camp/sampling_summary.csv") %>%
  rename(sample = X..surveys,
         buffer = X..buffer) %>% select(Stratification,sample,buffer,Population)%>% mutate(
           Stratification = Stratification %>% tolower() %>% str_replace_all("-","_") %>% str_replace_all(" ","_")  %>% str_replace_all("'","")
         ) %>% mutate(
           Stratification = case_when(Stratification == "bajet_kandala" ~ "bajed_kandala",
                                      Stratification == "berseve_1" ~ "bersive_1",
                                      Stratification == "berseve_2" ~ "bersive_1",
                                      Stratification == "dawadia" ~"dawoudia",
                                      Stratification == "qayyarah_jadah_5" ~ "qayyarah_jadah_five" ,
                                      T~Stratification)
         ) %>% rename(camp_name =Stratification)

############################################## TOOL ######################################################
tool_path <- "02_ToR_tools_Dap/01_tool/IRQ2206_Tool_MCNA X_transl_inc_CampProfiling_June 3rd_DEPLOYED.xlsx"
read_all_sheet_as_csv_format(tool_path)

############################################ date log ###################################################

date_log <- data %>% select(X_uuid,date_assessment)

if(write_file ==T){
write.csv(date_log,paste0("03_outputs/02_date_log/",str_replace_all(Sys.Date(),"-","_"),"_date_log.csv"))
write.csv(date_log,"03_outputs/02_date_log/date_log.csv")
}

daily_data <- data %>% filter(!X_uuid %in%  old_date_log$X_uuid)

indv_daily_data <- indv %>% filter(X_uuid %in% daily_data$X_uuid)


## Progress tracker
### Number of surveys by population group

progress_total <- data %>% group_by(pop_group,district,ngo_name) %>% summarise(
  survey_completed = n()
) %>% ungroup() 

############################################ HOST COMMUNITY ###########################################################
hc_progress <- progress_total %>% filter(pop_group == "hc") %>% select(district,survey_completed)

hc_progress_final <- hc_sf %>% left_join(hc_progress) %>% mutate(
  renaming = sample - survey_completed
)
############################################ Returnees ################################################################
ret_progress <- progress_total %>% filter(pop_group == "returnee") %>% select(district,survey_completed)

retu_progress_final <- returnees_sf %>% left_join(ret_progress) %>% mutate(
  renaming = sample - survey_completed
)


############################################ OUT CAMP IDPs ################################################################
out_camp_progress <- progress_total %>% filter(pop_group == "out_camp_idp") %>% select(district,survey_completed)

out_camp_progress_final <- out_idp_sf %>% left_join(out_camp_progress) %>% mutate(
  renaming = sample - survey_completed
)

############################################ IN CAMP IDPs ################################################################

progress_total_camp <- data %>% filter(pop_group == "in_camp_idp") %>% group_by(camp_name) %>% summarise(
  survey_completed = n()
) %>% ungroup() %>% mutate(
  camp_name = as.character(camp_name)
)

in_camp_progress_final <- in_idp_sf %>% left_join(progress_total_camp) %>% mutate(
  renaming = sample - survey_completed
)

### Number of surveys by NGOs
progress_by_NGO <- data %>% group_by(district,ngo_label) %>% summarise(
  completed_survey = n()
) %>% pivot_wider(id_cols = "district",names_from = "ngo_label",values_from = "completed_survey")

### Number of surveys per day per enumeratro
progress_by_enu <- data %>% group_by(date_assessment,enumerator_name_id,ngo_label) %>% summarise(
  completed_survey = n()
)

### NGO productivity
progress_by_NGO_productivity <- data %>% group_by(district,date_assessment,ngo_label) %>% summarise(
  completed_survey = n()
) 

### Enumerator productivity
#Enumerator who completed more than 5 surveys in a day/ less than 3 surveys in a day 

enumerator <- data %>% group_by(date_assessment,ngo_label,enumerator_name_id) %>% summarise(
  completed_survey = n()
) %>% filter(completed_survey <3 | completed_survey > 5)

```


```{r include=FALSE}
## HC MAP 
host_community_map_df <- admin2_boundary %>% left_join(hc_progress_final) %>% mutate(
  renaming = case_when(!is.na(as.numeric(sample)) & is.na(as.numeric(renaming))~0, T ~ as.numeric(renaming)),
  survey_completed = case_when(!is.na(as.numeric(sample)) & is.na(as.numeric(survey_completed))~0, T ~ as.numeric(survey_completed)),
  percentage_completed = (as.numeric(survey_completed)/as.numeric(sample))*100
) 

### Outcamp IDPs Map
out_idps_map_df <- admin2_boundary %>% left_join(out_camp_progress_final) %>% mutate(
  renaming = case_when(!is.na(as.numeric(sample)) & is.na(as.numeric(renaming))~0, T ~ as.numeric(renaming)),
  survey_completed = case_when(!is.na(as.numeric(sample)) & is.na(as.numeric(survey_completed))~0, T ~ as.numeric(survey_completed)),
  percentage_completed = (as.numeric(survey_completed)/as.numeric(sample))*100
) 

### Retunrnees

returnees_map_df <- admin2_boundary %>% left_join(retu_progress_final) %>% mutate(
  renaming = case_when(!is.na(as.numeric(sample)) & is.na(as.numeric(renaming))~0, T ~ as.numeric(renaming)),
  survey_completed = case_when(!is.na(as.numeric(sample)) & is.na(as.numeric(survey_completed))~0, T ~ as.numeric(survey_completed)),
  percentage_completed = (as.numeric(survey_completed)/as.numeric(sample))*100
) 


bins <- c(0, 10,20 ,40, 60, 80, 100)
pal_hc <- colorBin("Blues", domain = round(host_community_map_df$percentage_completed), bins = bins)
pal_out_camp <- colorBin("Blues", domain = round(out_idps_map_df$percentage_completed), bins = bins)
pal_returnees <- colorBin("Blues", domain =round( returnees_map_df$percentage_completed), bins = bins)


pop_hc <- case_when(!is.na(host_community_map_df$renaming) ~ paste("District:" ,"<b>", snakecase::to_sentence_case(host_community_map_df$district),"</b>", "<br>",
             "Survey Completed:", host_community_map_df$percentage_completed, "%" , "<br>",
             "Remaining:", host_community_map_df$renaming), T~ "NOT ASSESSED")


pop_returnee <- case_when(!is.na(returnees_map_df$renaming) ~ paste("District:" ,"<b>", snakecase::to_sentence_case(returnees_map_df$district),"</b>", "<br>",
             "Survey Completed:", returnees_map_df$percentage_completed, "%" , "<br>",
             "Remaining:", returnees_map_df$renaming), T~ "NOT ASSESSED")

pop_out_cmp <- case_when(!is.na(out_idps_map_df$renaming) ~ paste("District:" ,"<b>", snakecase::to_sentence_case(out_idps_map_df$district),"</b>", "<br>",
             "Survey Completed:", out_idps_map_df$percentage_completed, "%" , "<br>",
             "Remaining:", out_idps_map_df$renaming), T~ "NOT ASSESSED")


map <- leaflet::leaflet() %>% 
  leaflet::addPolygons(data = host_community_map_df,
                       stroke = T,
                       opacity = 1,
                       fillOpacity = .5,
                       smoothFactor = .5,
                       color = "#58585A",
                       fillColor =~pal_hc(round(percentage_completed)),
                       popup = pop_hc,
                       weight = 1,group = "Host community") %>% 
  leaflet::addPolygons(data = out_idps_map_df,
                       stroke = T,
                       opacity = 1,
                       fillOpacity = .5,
                       smoothFactor = .5,
                       color = "#58585A",
                       fillColor = ~pal_out_camp(round(percentage_completed)),
                       popup = pop_out_cmp,
                       weight = 1,group = "Out camp IDPs") %>% 
  leaflet::addPolygons(data = returnees_map_df,
                       stroke = T,
                       opacity = 1,
                       fillOpacity = .5,
                       smoothFactor = .5,
                       color = "#58585A",
                       fillColor =~pal_returnees(round(percentage_completed)),
                       popup = pop_returnee,
                       weight = 1,group = "Returnees") %>% 
  addLayersControl(baseGroups  = c("Host community","Out camp IDPs","Returnees"),
                   options = layersControlOptions(collapsed = F)) %>%  hideGroup(c("Out camp IDPs","Returnees"))
  
  

```



```{r include = FALSE, eval=TRUE}
all_cleaning_log <- list()

source("04_script/07_functions.R")
#### DATA CLEANING

###################################### CHECK OTHERS ##########################################

text_cols <- (survey %>% filter(type == "text"))$name[!(survey %>% filter(type == "text"))$name%in% c( "enumerator_name" ,"contact_details_name", "referral_contact", "referral_name","contact_details_telephone") ]
text_cols_hh <- text_cols[text_cols %in% names(daily_data)]

others_hh <- daily_data %>% select(X_uuid,text_cols_hh) %>% pivot_longer(cols = text_cols_hh,names_to = "question",values_to = "old_value") %>% filter(!is.na(old_value)) %>% mutate(
  issue = "others"
) %>% mutate_all(as.character)


text_cols_indv <- text_cols[text_cols %in% names(indv_daily_data)]

others_indv <- indv_daily_data %>% select(X_uuid,text_cols_indv) %>% pivot_longer(cols = text_cols_indv,names_to = "question",values_to = "old_value") %>% filter(!is.na(old_value)) %>% mutate(
  issue = "others"
) %>% mutate_all(as.character)


others_cl <- others_hh %>% left_join(others_indv)

others_cl_a <- others_cl %>% mutate(
  parent_question_for_other = case_when(grepl( "_other", question) ~ str_replace_all(question,"_other",""))
) %>% left_join(survey %>% select(name,type) %>% rename(parent_question_for_other= name)) %>% mutate(
  choice_list = sub(".* ","",type),
  type_only = sub(" .*","", type)
)



surve_with_type <- survey %>% mutate(
  list_name = sub(".* ","",type)
) %>% select(name,type, list_name) %>% rename(
  name_srvy=name 
)

choice_with_type <- choices %>% left_join(surve_with_type) %>% select(list_name,type,name,name_srvy) %>% mutate(
  name = case_when(grepl("select_multiple",type)~ paste0(name_srvy,".",name),
                   T~name)
)



choice_list <- choice_with_type %>% group_by(list_name) %>% summarise(
  choice_list_from_kobo = paste0(name,collapse=",")
)

all_cleaning_log[["others"]] <- others_cl_a %>% dplyr::left_join(choice_list,by=c("choice_list" = "list_name" )) %>% select(c("X_uuid", "question", "old_value", "issue", "choice_list_from_kobo"))


#################################### Similarity checks #####################################

survey_similarity <- calculateDifferences(data, survey) %>% select(X_uuid,n.col.not.NA, survey.id,number.different.columns)
# enum_similarity <- calculateEnumeratorSimilarity(data, survey, col_enum = "enumerator_name_id", col_admin = "district")

survey_similarity <- survey_similarity %>% left_join(data %>% select(X_uuid,enumerator_name_id,ngo_label))

if(write_file ==T){
write.csv(survey_similarity,paste0("03_outputs/04_survey_similarity/", str_replace_all(Sys.Date(),"-","_"),"_cleaning_log.csv"))
}
##################################### duration check #####################################

audit_node <- "/aMDiXwA6KtooKc5j5Ktcyp/"
audit_file <- paste0("01_inputs/05_audit/","aMDiXwA6KtooKc5j5Ktcyp","_",str_replace_all(Sys.Date(),"-","_"),".zip")
path_unzip <- paste0("03_outputs/03_audit_temp/", str_replace_all(Sys.Date(),"-","_"), ".zip")

audit_yes <- load_audit(data = data,path.to.zip = audit_file,
                         copy.zip = F,filter.column = "consent",
                         filter.on = "yes",path.to.unzip = path_unzip)

quick_survey(df = data,consent_column_name = "consent",audit_node = audit_node,uuid_col_name = "X_uuid",
                         audit_yes = audit_yes,start_question_node = "consent",end_question_node = "contact_group/further_contact_willing" ,min_allowable_duration = 0 )


enumerator_duration <- surveys_with_duration %>% left_join (data %>% select(X_uuid,enumerator_name_id,ngo_label,pop_group,district),by =c("uuid"="X_uuid"))

mean_median_duration_by_pop_grp <- enumerator_duration %>% group_by(pop_group) %>% summarise(
  mean = mean(duration_minutes,na.rm =T),
  median = median(duration_minutes,na.rm =T)
)


duration_by_enumerator <- enumerator_duration %>% group_by(enumerator_name_id,ngo_label,pop_group,district) %>% summarise(
  number_of_competed_survey = n(),
  mean_survey_duration = mean(duration_minutes,na.rm=T),
  median_survey_duration = median(duration_minutes,na.rm=T),
) %>% arrange(mean_survey_duration)


hc_median_duration <- (mean_median_duration_by_pop_grp %>% filter(pop_group     == "hc"))$median
returnees_median_duration <- (mean_median_duration_by_pop_grp %>% filter(pop_group     == "returnee"))$median
out_idp_median_duration <- (mean_median_duration_by_pop_grp %>% filter(pop_group     == "out_camp_idp"))$median
in_idp_median_duration <- (mean_median_duration_by_pop_grp %>% filter(pop_group     == "in_camp_idp"))$median


enumerator_duration %>% left_join(mean_median_duration_by_pop_grp)

all_cleaning_log[["duration"]] <-  enumerator_duration %>% left_join(mean_median_duration_by_pop_grp) %>%
   filter(duration_minutes < (median -10)) %>% 
   mutate(
     issue = paste0("Survey completed in less than [",median-10 ,"] (median duration-10 min) min")) %>% 
   select(uuid,duration_minutes, issue) %>% rename("X_uuid" = "uuid",
                                                   "old_value"="duration_minutes")  %>% mutate_all(as.character)
 


############################ Location check ###################################


hc_sp <- st_read("03_outputs/01_sampling/03_sample_point/01_host_community/01_map_and_kml/full_map/HC_sample_point_all.shp")
out_camp_idp_sp <- st_read("03_outputs/01_sampling/03_sample_point/02_IDPs/02_out_camp/total/all_point.kml")
file_list <- list.files("03_outputs\\01_sampling\\03_sample_point\\02_IDPs\\01_in_camp",pattern = ".ini",full.names = T)
unlink(file_list)
in_camp_idp_sp <- merge_kml(input_folder = "03_outputs\\01_sampling\\03_sample_point\\02_IDPs\\01_in_camp")
returnee_sp <- st_read("03_outputs/01_sampling/03_sample_point/03_Returnees/total/all_points.kml")

daily_data_sf <- st_as_sf(daily_data, coords = c("X_gpslocation_longitude","X_gpslocation_latitude"),crs = 4326)

dt_with_distance <- list()

# c("hc_sp","out_camp_idp_sp","in_camp_idp_sp","returnee_sp")
for (i in "out_camp_idp_sp") {
  df_location <-daily_data_sf %>% filter(pop_group == str_replace_all(i,"_sp","")) %>% st_transform(32638) 
  target_sp <- get(i) %>% st_transform(32638)
  dt_with_distance[["out_camp_returnee"]] <-  mutate_nearest_feature(x = df_location,y = target_sp ) %>% mutate(
  issue = paste0("Distance between surveyed point and nearest target point (index:", y_index, ") is grater than 1 km")) %>%  
     rename(old_value = distance) %>% mutate(
      old_value = old_value %>% as.numeric()
    ) %>% filter(old_value > 1000) %>% mutate(
      old_value = paste0(old_value," [m]")
    )
  }

location_outside_buffer <- do.call("bind_rows",dt_with_distance) %>% st_transform(4326)

all_cleaning_log[["distance_check"]] <- location_outside_buffer %>% as.data.frame() %>%  select(X_uuid,issue, old_value)  %>% mutate_all(as.character)


### potential distance issue 


quakeIcons <-  makeIcon("http://maps.google.com/mapfiles/ms/icons/red.png", iconWidth = 32, iconHeight =32)


map_distance <- leaflet::leaflet() %>% 
  leaflet::addProviderTiles(providers$Esri.WorldImagery,group = "ERSI World Imagery") %>% 
  leaflet::addProviderTiles(providers$OpenStreetMap.HOT,group = "OSM") %>% 
  leaflet::addMarkers(data = location_outside_buffer,
                      icon = ~quakeIcons,
                      popup = ~ paste0("UUID:", X_uuid, "<br>",
                                       "Pop group:", pop_group, "<br>",
                                       "District:", district)) %>% 
  addLayersControl(baseGroups = c("OSM","ERSI World Imagery"))
                                       


############################### outliers checks ####################################


outlier_hh <- illuminate::outlier_check(df = data,kobo_tool_location = tool_path,cols_to_report = "X_uuid",include_multiple_choices = F)
outlier_indv <- illuminate::outlier_check(df = indv,kobo_tool_location = tool_path,cols_to_report = c("X_uuid","repeat_uuid"),include_multiple_choices = F)

outliers <- outlier_hh %>% bind_rows(outlier_indv) %>% rename(
  question = questions
)

all_cleaning_log[["outliers"]] <- outliers %>% filter(!X_uuid %in% old_date_log$X_uuid) %>% mutate_all(as.character)


########## ceck for multiple Hoh ######################

multi_hoh<- indv_daily_data %>% filter(relationship == "head") %>% group_by(X_uuid) %>% summarise(
  head_count = n()
)  %>% ungroup()

df_multiple_hoh <- daily_data %>% left_join(multi_hoh) %>% filter(head_count != 1 | is.na(head_count)) %>% mutate(
  issue = "Multiple Head of household or No head of household reported"
) %>% select(X_uuid,issue,head_count) %>% rename(old_value = head_count)

all_cleaning_log[["multi_hoh_daily_hh"]]  <- df_multiple_hoh %>% mutate_all(as.character)

######### check hoh gender and spous hoh ##############

multiple_hoh_uuid <- df_multiple_hoh$X_uuid

indv_head_gender <- indv_daily_data %>% filter(!X_uuid %in% multiple_hoh_uuid ) %>% filter(relationship == "head") %>% mutate(
  hoh_gender_indv = sex_member,
  hoh_age_indv =    age_member
) %>% select(X_uuid,hoh_gender_indv,hoh_age_indv)

daily_data <- daily_data %>% left_join(indv_head_gender) %>% mutate(
  hoh_gender = case_when(hhh == "yes"  ~ gender_respondent,T~hoh_gender_indv),
  hoh_age = case_when(hhh == "yes"  ~ age_respondent,T~hoh_age_indv),
) 


spous_data <- indv_daily_data %>% filter(relationship == "spouse") %>% group_by(X_uuid) %>% summarise(
  spouse_gender = paste0(sex_member,collapse = ","),
  spouse_age = paste0(age_member,collapse = ",")
)

daily_data<- daily_data %>% left_join(spous_data)


uuid_spous <- daily_data %>% mutate(
  spous_gender_multiple = case_when(grepl(pattern = ",",spouse_gender) ~ "need_checking",T~"ok")
) %>% filter(spous_gender_multiple == "need_checking") %>% mutate(
  spous_gender_class = lengths(lapply(strsplit(spouse_gender, split = ','), unique))
) %>% filter(spous_gender_class >1)



uuid_spouse_different_gender<- uuid_spous$X_uuid

all_cleaning_log[["spouse_gender_dif"]] <- indv_daily_data %>% filter(relationship == "spouse" & X_uuid %in% uuid_spouse_different_gender) %>% 
  select(X_uuid,repeat_uuid,sex_member) %>% pivot_longer(cols = sex_member,names_to = "question",values_to = "old_value") %>% 
  mutate(issue = "Mutiple of spouse and the gender of spouses are different")  %>% mutate_all(as.character)




############################### Logical checks ##################################


logic <- read.csv("01_inputs/06_logical_check/conditions_log.csv")

if( !"in_camp_idp" %in% unique(daily_data$pop_group)){
  logic <- logic %>% filter(id != 8)

} else{
    daily_data$arrival_displace_date_diff_camp  <-(anytime::anydate(daily_data$arrival_date_idp_camp)-anytime::anydate(daily_data$displace_date_idp_camp))  %>% as.numeric(units = "days")
}


if(! "out_camp_idp" %in% unique(daily_data$pop_group)){
  logic <- logic %>% filter(id != 7)

} else{

daily_data$arrival_displace_date_diff_idp  <-(anytime::anydate(daily_data$arrival_date_idp)-anytime::anydate(daily_data$displace_date_idp))  %>% as.numeric(units = "days")}

daily_data$start_time <- daily_data$start %>% lubridate::as_datetime(format = '%d/%m/%Y %H:%M',tz = "") %>% strftime(format="%H.%M") %>% as.numeric()


all_cleaning_log[["logical_checks"]] <- illuminate::logical_check(df = daily_data,uuid = "X_uuid",logic_list_df = logic,logic_col_name = "conditions",add_description = T,col_name_issue = "issue_label") %>% mutate_all(as.character)



##### coping mehanism for food security

diff_cols <- c("difficulty_seeing","difficulty_hearing","difficulty_walking","difficulty_remembering","difficulty_selfcare","difficulty_communicating")
diff_choices <-  c("some_difficulty","a_lot_of_difficulty","cannot_do_at_all")

all_cleaning_log[["difficulties"]] <- indv_daily_data %>%  mutate(
  dif_rs = rowSums(indv_daily_data[,diff_cols] == "some_difficulty" | indv_daily_data[,diff_cols] == "a_lot_of_difficulty" | indv_daily_data[,diff_cols] == "cannot_do_at_all"  , na.rm = T)
) %>% filter(dif_rs > 4) %>% select(X_uuid,repeat_uuid,diff_cols) %>% pivot_longer(cols = !c("X_uuid","repeat_uuid"),names_to = "question",values_to = "old_value") %>% mutate(
  issue = "Person with atleast five difficulties"
) %>% mutate_all(as.character)



Cleaning_log_final <- do.call("bind_rows", all_cleaning_log) %>% mutate(
  loop = case_when(question %in% names(data) ~ "hh", 
                   question %in% names(indv) ~ "indv")
)

Cleaning_log_final <- Cleaning_log_final %>% filter(!X_uuid %in% old_date_log$X_uuid) %>%  left_join(data %>%
                                                                                                  select(X_uuid,enumerator_name_id,ngo_label,pop_group,district,camp_name,contact_details_telephone))

survey_label <- survey %>% select(name,`label::English`,`label::Arabic`) %>% rename(
  question = name
)

Cleaning_log_final <- Cleaning_log_final %>% left_join(survey_label)


Cleaning_log_final <- Cleaning_log_final %>% 
  select(X_uuid,repeat_uuid,enumerator_name_id,ngo_label,loop,question,`label::English`,`label::Arabic`,issue,choice_list_from_kobo,pop_group,district,camp_name,contact_details_telephone,old_value) %>% 
  group_by(X_uuid,issue) %>% mutate(
  id = cur_group_id()
) 





write_list <- list(Cleaning_log_final= "Cleaning_log_final",
                   daily_data ="daily_hh",
                   indv_daily_data = "daily_indv")
if(write_file ==T){
write_excel_as_reach_format(write_list,paste0("03_outputs/05_daily_cleaning_before_feedback/", str_replace_all(Sys.Date(),"-","_"),"_cleaning_log.xlsx"),cols_for_color = "id")
}
```









# {.tabset}

***

## Survey Meta data

Total number of completed survey - `r total_survey` </br>
Consent Yes - `r yes_consent` </br>
Consent No- `r no_consent`</br>
Not elegible - `r not_eleigible`</br>
Total elegible - `r eleigible`</br>


```{r  eval=TRUE, echo=FALSE, results='asis'}

kable(group_by_pop_grp,longtable = T, booktabs = T, linesep = "",caption= "Total number of completed survey by population group")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = T)



DT::datatable(mean_median_duration_by_pop_grp,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top",caption = "Duration summary by population group"
              )

DT::datatable(survey_similarity,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top",caption = "Survey Similarity"
              )






```


## Progress in Map
<center>**Progress**</center>

```{r eval=TRUE, out.width = '100%',echo=FALSE, results='asis'}
map
```
## NGO Progress

<center>**Completed Interviews**</center>

```{r eval=TRUE, echo=FALSE, results='asis'}

kable(progress_by_NGO,longtable = T, booktabs = T, linesep = "",caption= "Number of completed survey by NGO")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = T)
```

<center>**NGO productivity**</center>
```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(progress_by_NGO_productivity,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top",caption = "Number of completed survey by NGO by date"
              )
```

***


***
## Enumerator behaviour checks

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(enumerator,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top",caption = "Enumerator who completed more than 5 surveys in a day/ less than 3 surveys in a day "
              )


DT::datatable(progress_by_enu,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top",caption = "Number of survey by enumerator"
              )



DT::datatable(duration_by_enumerator,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top",caption = "Survey duration by enumerator by population group"
              )



# 
# DT::datatable(enum_similarity,
#               options = list(
#                   pageLength = 130,
#                   dom = 't',
#                   autoWidth = F),
#               rownames = F,
#               filter = "top",caption = "Enumerator Similarity checks"
#               )

```
***


***
## In-camp IDP Progress
```{r eval=T, echo=FALSE, results='asis'}
DT::datatable(in_camp_progress_final,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top"
              )
```

***

***
## Out-camp IDP Progress
```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(out_camp_progress_final,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top"
              )
```

***

***
## Returnees IDP Progress
```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(retu_progress_final,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top"
              )
```

***

***
## Host coummunity Progress
```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(hc_progress_final,
              options = list(
                  pageLength = 130,
                  dom = 't',
                  autoWidth = F),
              rownames = F,
              filter = "top"
              )
```

***

***
## Location check
<center>**Distance between target and survey points iS greater than one km**</center>

```{r eval=TRUE, out.width = '100%',echo=FALSE, results='asis'}
map_distance
```
***

***
## Necessary links


* [Daily progress tracker](https://drive.google.com/drive/folders/1db369W5zoELlLIAuqqKPAEcpJbYAadWh?usp=sharing)

* [Daily cleaning log before feedback](https://drive.google.com/drive/folders/1darC01z0YxuLuhD4oP0PYbeyHEy-G1dd?usp=sharing)

* [How to fill the cleaning log](https://docs.google.com/spreadsheets/d/1pilA4UzXHUOPCiAo1EcbZsiRRaL0KkJL/edit?usp=sharing&ouid=114082038892110807915&rtpof=true&sd=true) 

* [Daily cleaning log after feedback](https://drive.google.com/drive/folders/1db256lliKTJ5FiMtel_xUvS4VoEwugFc?usp=sharing)

* [Survey Similarity](https://drive.google.com/drive/folders/1b4TLxsAf5Y80FAH3bMce9pknNUMF53Hw?usp=sharing)


***


